\Title

### 2015-10-13 moho-inversion.tex
Initial text to botts method

\begin{equation}
    \mbf{H}^k\mbf{\Delta p} = -\mbf{\nabla}\Gamma^k,
\end{equation}

@@

>>>>

\begin{equation}
    \mbf{H}^k\mbf{\Delta p} = -\mbf{\nabla}\Gamma^k,
    \label{eq:gaussnewton}
\end{equation}

@@

\citet{bott_use_1960} developed an efficient method to determined the basement
relief of a sedimentary basin from gravity observations.
The method requires data on a regular grid of $N_x \times N_y = N$
observations.
The method discretizes the basement relief into an equal grid of $N_x \times
N_y$ elements.
The method starts with an initial estimate of the basement relief
$\mbf{p}^0$ equal to the null vector and updates the estimate using the formula

\begin{equation}
    \mbf{\Delta p} = \dfrac{\mbf{d}^o - \mbf{d}(\mbf{p}^k)}{2\pi G \Delta \rho},
    \label{eq:bott}
\end{equation}

\noindent
in which $G$ is the gravitational constant and $\Delta \rho$ is the basin
density contrast.
The iterative process stops when the inversion residuals
$\mbf{r} = \mbf{d}^o - \mbf{d}(\mbf{p}^k)$ fall below the assumed noise level
of the data.

\citet{silva_fast_2014} showed that Bott's method can be formulated as
the Gauss-Newton method (\eq{gaussnewton})
by setting the Jacobian matrix to

\begin{equation}
    \mbf{A} = 2\pi G \Delta \rho \mbf{I},
    \label{eq:bott-jacobian}
\end{equation}

\noindent
in which $\mbf{I}$ is the identity matrix.
In this framework, Bott's method uses a Bouguer plate approximation to
linearize the Jacobian matrix.
Bott's method maintains the non-linearity of the predicted data
$\mbf{d}(\mbf{p}^k)$.

Bott's method can also be formulated as the Steepest Descent method
(\eq{steepest}) by setting the Jacobian matrix to

\begin{equation}
    \mbf{A} = \dfrac{1}{4 \pi G \Delta \rho}\mbf{I}.
    \label{eq:bott-steepest}
\end{equation}
